Exploring Molecular Conformations and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation

### 2013-08-09 writedown/npt-neq/alanine.tex
add orientational discussion

\subsection{System settings and simulation protocol}
\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
  % \\
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
  \caption{The
    $x$-component of the dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The dashed line presents the strengths of the
    external electric field, while the solid line presents the dipole
    moments. }
  \label{fig:tmp3}
\end{figure}

@@

\subsection{Results and discussions}
\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-meta-npt.eps}
  \caption{The probability of being in a metastable states under a constant EF.
    The warm-up time $t_{init} = 10$~ps. The red line stands for state $A_1$,
    green for $A_2$, dark blue for $B_1$, purple for $B_2$ and light blue
    for $C$.
  }
  \label{fig:tmp5}
\end{figure}

@@

The Fig.~\ref{fig:tmp3}
shows that the $x$-component of the dipole moment of the alanine dipeptide
reaches 85\% of the maximum value in only 20~ps, which is comparable to
the warm-up time $t_{init}$. Then the dipole slowly relaxes to the 
maximum value in the following 400~ps. Notice that 20~ps is 25 times
smaller than the slowest time scale of the conformational relaxation.
This indicate that when the EF is switched on, the alanine almost immediately
align itself to the
direction of the external EF without much conformational change.
And then, the conformation is slowly adjusted according to the
external field (now it is the same as the molecular dipole),
finally  the new equilibrium is reached at a much slower time scale
(approximately 500~ps).

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-mode2-dipol.eps}
  \caption{The nonequilibrium dipole moment of alanine dipeptide as a
    function of time. Only the $x$-component of the dipole moment is
    shown here. The black line: the static electric field with turning on
    time $t_{init} = 10$~ps. The red line: oscillating field with period
    10~ps. The green line: period 40~ps. The blue line: period 200~ps.}
  \label{fig:tmp8}
\end{figure}

Fig.~\ref{fig:tmp8} presents the $x$-component of the molecular dipole moment as
a function of time. The red, green and blue lines stands for the
results of $T=10$~ps, 40~ps and 200~ps, respectively. The black lines
shows the dipole moment under constant electric field
for reference.
It demonstrates that the periods of the molecular dipole moment
is the same as the periods of the oscillating EF. Therefore,
the molecular dipole moment
is able to response to the external EF almost immediately.
At $T=200$~ps, the maximum magnitude of the molecular
dipole moment is almost the same as the case of constant electric field, which
means that the changing of the electric field is so slow that the
alanine have enough time to firstly align to the external EF, and then
relax its internal dipole (although not completely). However,
for $T=40$~ps, as the electric field changes faster,
although the molecules can align to the electric field immediately,
it does not have enough time to fully relax the internal dipole, so we
see the maximum alanine's dipole moment reached is smaller.
For even smaller period $T=10$~ps, the alanine does not have enough
time  to properly align the molecular dipole according to the external
field, so we see the maximum dipole moment is only about one third of the
constant EF case.

>>>>

\subsection{System settings and simulation protocol}

@@

\subsection{Results and discussions}

\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
  % \\
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
  \caption{The
    $x$-component of the dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The dashed line presents the strengths of the
    external electric field, while the solid line presents the dipole
    moments. }
  \label{fig:tmp3}
\end{figure}

The Fig.~\ref{fig:tmp3}
shows that the $x$-component of the dipole moment of the alanine dipeptide
reaches 85\% of the maximum value in only 20~ps, which is comparable to
the warm-up time $t_{init}$. Then the dipole slowly relaxes to the 
maximum value in the following 400~ps. Notice that 20~ps is 25 times
smaller than the slowest time scale of the conformational relaxation.
We also consider the orientation of the alanine dipeptide as a function
of time. The geometric direction of the alanine is defined by the red vector in
Fig.~\ref{fig:tmp3}, which is the angle bisector of the two black vectors.
The black vectors are define to connect the $\alpha$-carbon and the carbons
on the methyl groups. We define the orientational order parameter
\begin{align}
  S_\theta = \langle 3\sin^2\theta - 2\rangle,
\end{align}
where $\theta$ is the angle between the orientation of the alanine dipeptide
and the direction of the electric field. The order parameter
indicate if the molecule is perpendicular to the electric field.
If the molecule is perfectly perpendicular to the electric field, then $S_\theta = 1$;
If the molecule has no directional
preference at all, then $S_\theta = 0$;
If the molecule is perfectly parallel to the electric field, then $S_\theta = -2$.
From $t=0$ to roughly 10~ps, the orientational order parameter fastly
decreases from 0 to -0.15, which means a weak alignment of the molecule to the external field.
Then from $t=0$ to 500~ps, the molecule slowy changes to the orientation
that is perpendicular to the electric field.

% This indicate that when the EF is switched on, the alanine almost immediately
% changes its conformation so that the molecular dipole is aligned to the
% external EF.
% align itself to the
% direction of the external EF without much conformational change.
% And then, the conformation is slowly adjusted according to the
% external field (now it is the same as the molecular dipole),
% finally  the new equilibrium is reached at a much slower time scale
% (approximately 500~ps).

\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-meta-npt.eps}
  \caption{The probability of being in a metastable states under a constant EF.
    The warm-up time $t_{init} = 10$~ps. The red line stands for state $A_1$,
    green for $A_2$, dark blue for $B_1$, purple for $B_2$ and light blue
    for $C$.
  }
  \label{fig:tmp5}
\end{figure}

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{fig.ala/fig-mode2-dipol.eps}
  \includegraphics[width=0.48\textwidth]{fig.ala/fig-mode2-order.eps}
  \caption{The nonequilibrium dipole moment (a) and
    orientation order parameter (b) of alanine dipeptide as a
    function of time. In plot (a),
    only the $x$-component of the dipole moment is
    shown. The black line: the static electric field with turning on
    time $t_{init} = 10$~ps. The red line: oscillating field with period
    10~ps. The green line: period 40~ps. The blue line: period 200~ps.}
  \label{fig:tmp8}
\end{figure}

Fig.~\ref{fig:tmp8} (a)
presents the $x$-component of the molecular dipole moment as
a function of time. The red, green and blue lines stands for the
results of $T=10$~ps, 40~ps and 200~ps, respectively. The black lines
shows the dipole moment under constant electric field
for reference.
It demonstrates that the periods of the molecular dipole moment
is the same as the periods of the oscillating EF. Therefore,
the molecular dipole moment
is able to response to the external EF almost immediately.
At $T=200$~ps, the maximum magnitude of the molecular
dipole moment is almost the same as the case of constant electric field, which
means that the changing of the electric field is so slow that the
alanine have enough time to 
relax its internal dipole (although not completely). However,
for $T=10$ and 40~ps, as the electric field changes faster,
although the alanine dipeptide can response to the electric field immediately,
it does not have enough time to fully relax the internal dipole, so we
see the maximum alanine's dipole moment reached is smaller.
% For even smaller period $T=10$~ps, the alanine does not have enough
% time  to properly align the molecular dipole according to the external
% field, so we see the maximum dipole moment is only about one third of the
% constant EF case.
Plot (b) of Fig.~\ref{fig:tmp9} presents the orientational order
parameter. The notations are the same as plot (a).
% From the constant
% EF simulation, we see that the response of order parameter has
% two time scales: In the fast time scale, the 
For all periodically oscillating cases the order parameter is much
smaller than the constant EF case. One possible reason is that the
relaxation of the order parameter is very slow, and the molecule does
not expose to a strong enough EF for a long enough time in a oscillating
EF. For  $T=10$ and 40~ps, the orientation of the alanine is only weakly
parallel to the EF. Please notice that for the constant EF case,
we also observe a quit alignment of molecular orientation to the EF
at time scale 10~ps. For $T=200$~ps, The molecule periodically
becomes perpendicular to the EF, but this directional preference is much
weaker than the constant EF case.
